Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of Strategies in the Moran process for the Iterated Prisoner's Dilemma

### 2018-04-06 plos/main.tex
Include ranks v population size in main text.

In this section the focus is on the ability of a mutant strategy to invade: the
probability of one individual of a given type successfully fixating in a
population of \(N - 1\) other individuals, denoted by \(x_1\).

@@

\subsubsection*{Strong resistors}

In addition to identifying good invaders, strategies resistant to invasion by
other strategies are identified by examining the distribution of $x_{N-1}$ for
each strategy.

@@

>>>>

In this section the focus is on the ability of a mutant strategy to invade: the
probability of one individual of a given type successfully fixating in a
population of \(N - 1\) other individuals, denoted by \(x_1\). The ranks of each
strategy for all considered values of \(N\) according to mean \(x_1\) are shown
in Fig~\ref{fig:ranks_v_size_invade}.

@@

\subsubsection*{Strong Resistors}

In addition to identifying good invaders, strategies resistant to invasion by
other strategies are identified by examining the distribution of $x_{N-1}$ for
each strategy. The ranks of each strategy for all considered values of \(N\)
according to mean \(x_{N-1}\) are shown in Fig~\ref{fig:ranks_v_size_resist}.

@@

Fig~\ref{fig:ranks_v_size_coexist} complements
Figs~\ref{fig:ranks_v_size_invade} and~\ref{fig:ranks_v_size_resist} showing the
ranks of each strategy for all considered even values of \(N\) according to mean
\(x_{N/2}\).
